---
title: "MUSA508 HW1: Queens TOD Markdown"
author: "Juliana Zhou (Collaborator: Julian Hartwell)"
date: "September 25, 2020"
output: 
  html_document:
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    number_sections: true
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	echo = FALSE)
library(tidyverse)
library(tidycensus)
library(sf)
library(kableExtra)
library(viridis)
library(RSocrata)
library(rmarkdown)

options(scipen=999)
options(tigris_class = "sf")

```

```{r styles, message=FALSE, include=FALSE}
mapTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 16,colour = "black"),
    plot.subtitle=element_text(face="italic"),
    plot.caption=element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2),
    strip.text.x = element_text(size = 14))
}

plotTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 16,colour = "black"),
    plot.subtitle = element_text(face="italic"),
    plot.caption = element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_line("grey80", size = 0.1),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2),
    strip.background = element_rect(fill = "grey80", color = "white"),
    strip.text = element_text(size=12),
    axis.title = element_text(size=12),
    axis.text = element_text(size=10),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"),
    strip.text.x = element_text(size = 14)
  )
}

# Load Quantile break functions

qBr <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(quantile(round(df[[variable]],0),
                          c(.01,.2,.4,.6,.8), na.rm=T))
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]]), digits = 3),
                 c(.01,.2,.4,.6,.8), na.rm=T)
  }
}

q5 <- function(variable) {as.factor(ntile(variable, 5))}

# Load hexadecimal color palette

palette5 <- c("#f0f9e8","#bae4bc","#7bccc4","#43a2ca","#0868ac")

# Load multiple ring buffer function

multipleRingBuffer <- function(inputPolygon, maxDistance, interval) 
{
  #create a list of distances that we'll iterate through to create each ring
  distances <- seq(0, maxDistance, interval)
  #we'll start with the second value in that list - the first is '0'
  distancesCounter <- 2
  #total number of rings we're going to create
  numberOfRings <- floor(maxDistance / interval)
  #a counter of number of rings
  numberOfRingsCounter <- 1
  #initialize an otuput data frame (that is not an sf)
  allRings <- data.frame()
  
  #while number of rings  counteris less than the specified nubmer of rings
  while (numberOfRingsCounter <= numberOfRings) 
  {
    #if we're interested in a negative buffer and this is the first buffer
    #(ie. not distance = '0' in the distances list)
    if(distances[distancesCounter] < 0 & distancesCounter == 2)
    {
      #buffer the input by the first distance
      buffer1 <- st_buffer(inputPolygon, distances[distancesCounter])
      #different that buffer from the input polygon to get the first ring
      buffer1_ <- st_difference(inputPolygon, buffer1)
      #cast this sf as a polygon geometry type
      thisRing <- st_cast(buffer1_, "POLYGON")
      #take the last column which is 'geometry'
      thisRing <- as.data.frame(thisRing[,ncol(thisRing)])
      #add a new field, 'distance' so we know how far the distance is for a give ring
      thisRing$distance <- distances[distancesCounter]
    }
    
    
    #otherwise, if this is the second or more ring (and a negative buffer)
    else if(distances[distancesCounter] < 0 & distancesCounter > 2) 
    {
      #buffer by a specific distance
      buffer1 <- st_buffer(inputPolygon, distances[distancesCounter])
      #create the next smallest buffer
      buffer2 <- st_buffer(inputPolygon, distances[distancesCounter-1])
      #This can then be used to difference out a buffer running from 660 to 1320
      #This works because differencing 1320ft by 660ft = a buffer between 660 & 1320.
      #bc the area after 660ft in buffer2 = NA.
      thisRing <- st_difference(buffer2,buffer1)
      #cast as apolygon
      thisRing <- st_cast(thisRing, "POLYGON")
      #get the last field
      thisRing <- as.data.frame(thisRing$geometry)
      #create the distance field
      thisRing$distance <- distances[distancesCounter]
    }
    
    #Otherwise, if its a positive buffer
    else 
    {
      #Create a positive buffer
      buffer1 <- st_buffer(inputPolygon, distances[distancesCounter])
      #create a positive buffer that is one distance smaller. So if its the first buffer
      #distance, buffer1_ will = 0. 
      buffer1_ <- st_buffer(inputPolygon, distances[distancesCounter-1])
      #difference the two buffers
      thisRing <- st_difference(buffer1,buffer1_)
      #cast as a polygon
      thisRing <- st_cast(thisRing, "POLYGON")
      #geometry column as a data frame
      thisRing <- as.data.frame(thisRing[,ncol(thisRing)])
      #add teh distance
      thisRing$distance <- distances[distancesCounter]
    }  
    
    #rbind this ring to the rest of the rings
    allRings <- rbind(allRings, thisRing)
    #iterate the distance counter
    distancesCounter <- distancesCounter + 1
    #iterate the number of rings counter
    numberOfRingsCounter <- numberOfRingsCounter + 1
  }
  
  #convert the allRings data frame to an sf data frame
  allRings <- st_as_sf(allRings)
}

# Load census API key

census_api_key("dc04d127e79099d0fa300464507544280121fc3b", overwrite = TRUE)
```


## Introduction

For development policy experts, Queens makes for an interesting and unique case study because it contains both extremely dense urban areas along the subway lines, as well as more suburban neighborhoods that do not have easy access to subway transit. Additionally, from a sociological perspective, development in Queens is interesting because the county is one of the most diverse in the United States.

In this report, I attempt to determine the influence of transit-oriented development in Queens, NY by evaluating the differences between TOD and non-TOD areas across time. Due to New York City's density, the TOD area will be defined as Census tracts within 1/4 mile of a subway station. The specific analyses I will conduct are listed below.[^longnote]    
* Mapping TOD differences for 2009 and 2016 in --
    + Population
    + Median rent
    + Bachelor degree holders (% of population)
    + Poverty (% of population)
* Grouped bar plot of the above values across time and space for comparison purposes
* Table of the above data for interpretability purposes
* Graduate symbol maps showing differences across time in population and median rent within 1/4 mile of each subway station in Queens, for 2009 and 2016
* Line graph of median rent by distance from station, for 2009 and 2016
* Point-level robbery data in 2016, and its relationship to transit access and median rent

### Part 1: Preparing ACS and Map Data

The below maps show the MTA stations (Figure 1.1) used create a transit TOD buffer sone (Figure 1.2), and finally, the TOD tract areas that will be used to analyze our 4 key indicators. 

```{r Data Wrangling, echo=FALSE, message=FALSE, warning=FALSE}

# Get 2009 ACS 5-Year data

tracts09 <- 
  get_acs(geography = "tract", variables = c("B25026_001E","B02001_002E","B15001_050E",
                                             "B15001_009E","B19013_001E","B25058_001E",
                                             "B06012_002E"), 
          year=2009, state=36, county=081, geometry=T, output="wide") %>%
  st_transform('ESRI:102318') %>%
  rename(TotalPop = B25026_001E, 
         Whites = B02001_002E,
         FemaleBachelors = B15001_050E, 
         MaleBachelors = B15001_009E,
         MedHHInc = B19013_001E, 
         MedRent = B25058_001E,
         TotalPoverty = B06012_002E) %>%
  dplyr::select(-NAME, -starts_with("B")) %>%
  mutate(pctWhite = ifelse(TotalPop > 0, Whites / TotalPop,0), 
         pctBachelors = ifelse(TotalPop > 0, ((FemaleBachelors + MaleBachelors) / TotalPop),0),
         pctPoverty = ifelse(TotalPop > 0, TotalPoverty / TotalPop, 0),
         year = "2009") %>%
  dplyr::select(-Whites, -FemaleBachelors, -MaleBachelors, -TotalPoverty) 

# Get 2016 ACS 5-Year data

tracts16 <- 
  get_acs(geography = "tract", variables = c("B25026_001","B02001_002","B15001_050",
                                             "B15001_009","B19013_001","B25058_001",
                                             "B06012_002"), 
          year=2016, state=36, county=081, geometry=T, output="wide") %>%
  st_transform('ESRI:102318') %>%
  rename(TotalPop = B25026_001E, 
         Whites = B02001_002E,
         FemaleBachelors = B15001_050E, 
         MaleBachelors = B15001_009E,
         MedHHInc = B19013_001E, 
         MedRent = B25058_001E,
         TotalPoverty = B06012_002E) %>%
  dplyr::select(-NAME, -starts_with("B")) %>%
  mutate(pctWhite = ifelse(TotalPop > 0, Whites / TotalPop,0),
         pctBachelors = ifelse(TotalPop > 0, ((FemaleBachelors + MaleBachelors) / TotalPop),0),
         pctPoverty = ifelse(TotalPop > 0, TotalPoverty / TotalPop, 0),
         year = "2016") %>%
  dplyr::select(-Whites, -FemaleBachelors, -MaleBachelors, -TotalPoverty) 

# Combine 2009 and 2016 data

allTracts <- rbind(tracts09,tracts16)


# Read in all NYC subway station data 

MTAStops <- 
  rbind(
    st_read("https://data.cityofnewyork.us/resource/kk4q-3rt2.geojson") %>% 
      select(name, line)) %>%
  st_transform('ESRI:102318')

# Subset/select only MTA stations in Queens

QnsMTA <- MTAStops[tracts09,]

# Check QnsMTA stations

ggplot() + 
  geom_sf(data=st_union(tracts09)) +
  geom_sf(data=QnsMTA, 
          #aes(colour = Line), 
          show.legend = "point", size= 1) +
  #scale_colour_manual(values = c("orange","blue")) +
  labs(title="MTA Stops", 
       subtitle="Queens, NY", 
       caption="Figure 1.1") +
  mapTheme()

# Create buffers (in feet) around Queens MTA stations, then create union buffer

QnsMTA_buffer <- 
  rbind(
    st_buffer(QnsMTA, 1320) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend),
    st_union(st_buffer(QnsMTA, 1320)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))

# Visualize both buffers and union buffer using "facet_wrap" plot

ggplot() +
  geom_sf(data=QnsMTA_buffer) +
  geom_sf(data=QnsMTA, show.legend = "point") +
  facet_wrap(~Legend) + 
  labs(caption="Figure 1.2") +
  mapTheme()

# Create an sf object with ONLY the unioned buffer
buffer <- filter(QnsMTA_buffer, Legend=="Unioned Buffer")

# Create TOD & non-TOD areas using centroid join
# Includes 2009-2016 inflation rate for MedRent variable: 1.118

allTracts.group <- 
  rbind(
    st_centroid(allTracts)[buffer,] %>%
      st_drop_geometry() %>%
      left_join(allTracts) %>%
      st_sf() %>%
      mutate(TOD = "TOD"),
    st_centroid(allTracts)[buffer, op = st_disjoint] %>%
      st_drop_geometry() %>%
      left_join(allTracts) %>%
      st_sf() %>%
      mutate(TOD = "Non-TOD")) %>%
  mutate(MedRent.inf = ifelse(year == "2009", MedRent * 1.118, MedRent)) 

# Time/Space map of 2009 & 2016 TOD tracts

ggplot(allTracts.group)+
  geom_sf(data = st_union(tracts09))+
  geom_sf(aes(fill = TOD)) +
  scale_fill_manual(values = c("#bae4bc","#43a2ca"),
                    name = "TOD") +
  labs(title = "TOD Areas", 
       subtitle = "*No new MTA station additions between 2009 & 2016",
       caption="Figure 1.3") +
  facet_wrap(~year)+
  mapTheme() + 
  theme(plot.title = element_text(size=22))
```

### Part 2: TOD Indicator Maps

Using the data that were gathered and cleaned in Part 1, I map the four key indicators at the tract level, showing the outline of the TOD area for visual comparison.

#### Indicator 1: Population
Between 2009 and 2016, there has been a population increase within the TOD area, and a slight decrease in population in Northeastern Queens, far outside the TOD area, there the communites are much more suburban. In addition, there has also been a population increase along the western border of Queens, just across the East River from Manhattan. 

```{r indicator map 1, echo=FALSE}

# Indicator Map #1: Population in 2009 & 2016, showing TOD
ggplot(allTracts.group)+
  geom_sf(data = st_union(tracts09))+
  geom_sf(aes(fill = q5(TotalPop)), lwd = 0) +
  geom_sf(data = buffer, fill = "transparent", color = "red", size = 1)+
  scale_fill_manual(values = palette5,
                    labels = qBr(allTracts.group, "TotalPop"),
                    name = "Population\n(Quintile Breaks)") +
  labs(title = "Population in 2009 & 2016", 
       caption="Figure 2.1") +
  facet_wrap(~year)+
  mapTheme() + 
  theme(plot.title = element_text(size=22))
```

#### Indicator 2: Median Rent
As expected, as the population within the TOD area has increased, median rent as increased with it, even in far-flung neighborhoods like Far Rockaway (southernmost TOD area). Interestingly, although the population has decreased in the northeastern neighborhoods of Flushing, Bayside, Hollis, and Jamaica, median rent has risen. This may be due in part to increased rental activity in the area, where previously homeownership has been the norm. 

```{r indicator map 2, echo=FALSE}

# Indicator Map #2: Median rent in 2009 & 2016, showing TOD
ggplot(allTracts.group) + 
  geom_sf(data = st_union(tracts09))+
  geom_sf(aes(fill = q5(MedRent.inf)), lwd = 0) +
  geom_sf(data = buffer, fill = "transparent", color = "red", size = 1)+
  scale_fill_manual(values = palette5,
                    labels = qBr(allTracts.group, "MedRent.inf"),
                    name = "Median Rent ($)\n(Quintile Breaks)") +
  labs(title = "Median Rent 2009-2016", 
       subtitle = "Real Dollars", 
       caption="Figure 2.2") +
  facet_wrap(~year)+
  mapTheme() + 
  theme(plot.title = element_text(size=22))

```

#### Indicator 3: Poverty Rate
There has been a clear increase in the poverty rate between 2009 and 2016, most notably within the TOD are of central Queens (not Far Rockaway). In fact, the distribution of poverty appears to have shifted toward transit resources over this time span. 

```{r indicator map 3, echo=FALSE}

# Indicator Map #3: Poverty (% of TotalPop) in 2009 & 2016, showing TOD
ggplot(allTracts.group)+
  geom_sf(data = st_union(tracts09))+
  geom_sf(aes(fill = q5(pctPoverty)), lwd = 0) +
  geom_sf(data = buffer, fill = "transparent", color = "red", size = 1)+
  scale_fill_manual(values = palette5,
                    labels = qBr(allTracts.group, "pctPoverty"), 
                    name = "% Poverty\n(Quintile Breaks)") +
  labs(title = "Poverty 2009-2016", 
       subtitle="% of total population", 
       caption="Figure 2.3") +
  facet_wrap(~year)+
  mapTheme() + 
  theme(plot.title = element_text(size=22))

```

#### Indicator 4: Bachelor Degree Holders
The percent of residents with bachelor degrees has largely remained steady in much of Queens, with two exceptions. First, in the neighborhoods of Astoria and Long Island City, which are closest to midtown Manhattan, the percentage of bachelor degree holders has increased since 2009. Second, there has been a decrease in bachelor degree holders in the northeastern suburbs, coinciding with a decrease in population in that area as well.

```{r indicator map 4, echo=FALSE}

# Indicator Map #4: Bachelor Degree Holders in 2009 & 2016, showing TOD
ggplot(allTracts.group)+
  geom_sf(data = st_union(tracts09))+
  geom_sf(aes(fill = q5(pctBachelors)), lwd = 0) +
  geom_sf(data = buffer, fill = "transparent", color = "red", size = 1) +
  scale_fill_manual(values = palette5,
                    labels = qBr(allTracts.group, "pctBachelors"),
                    name = "% Bachelor Degree\n(Quintile Breaks)") +
  labs(title = "Bachelor Degree Holders 2009-2016", 
       subtitle="% of total population",
       caption="Figure 2.4") +
  facet_wrap(~year)+
  mapTheme() + 
  theme(plot.title = element_text(size=22))

```

### Part 3: Grouped Bar Plots

The bar plot shown below allows for comparison of aggregated TOD and non-TOD areas on the four key indicators. The percent of bachelor degree holders, while previously equal between TOD and non-TOD areas, has increased since 2009, but only near transit lines. Poverty, median rent, and population have all increased at a similar rate in both TOD and non-TOD areas.

```{r Part 3. TOD Grouped Bar Plots, echo=FALSE, message=FALSE}
# Create mean averages of variables
allTracts.Summary <- 
  st_drop_geometry(allTracts.group) %>%
  group_by(TOD, year) %>% # func to summarize by a number of factors
  summarize(Median_Rent = mean(MedRent, na.rm = T),
            Total_Pop = mean(TotalPop, na.rm = T),
            Percent_Bach = mean(pctBachelors, na.rm = T),
            Percent_Poverty = mean(pctPoverty, na.rm = T))

# Created grouped bar plot comparing:
# % bachelor's degree holders, % poverty rate, % white, total population, and median rent

allTracts.Summary %>%
  gather(Variable, Value, -year, -TOD) %>%
  ggplot(aes(year, Value, fill = TOD)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~Variable, scales = "free", ncol=5) +
  scale_fill_manual(values = c("#bae4bc", "#0868ac")) +
  labs(title = "Indicator differences across time and space",
       caption = "Figure 3.0") +
  plotTheme() + theme(legend.position="bottom")

```

### Part 4: Indicator Table

Adjusting for inflation, the median rent has increased by approximately $300 since 2009 in both TOD and non-TOD areas (in 2009 dollars).

```{r Part 4. TOD Indicator Tables, echo=FALSE, message=FALSE}

# Create comparison tables for indicator variables by TOD and year

kable(allTracts.Summary) %>%
  kable_styling() %>%
  footnote(general_title = "\n",
           general = "Table 4.0")

```

### Part 5: Population and Median Rent at Each Transit Stop

The below graduated symbol maps how the population and median income within a quarter mile of each MTA station. The most densely populated parts of the TOD area are in central Queens, possibly due to the relatively lower rent as compared to neighborhood that are closer to Manhattan. The graduated symbol map for median rent, however, shows a clear winner: Long Island City. The subway stops in this neighborhood, which are conveniently located to both Manhattan and Brooklyn, show median rents of over $2000.

```{r Part 5. Graduated Symbol Maps, echo=FALSE, message=FALSE}

# Create new sf object with 2016 tract data with 1/4 mile of Queens MTA stations

grad_buffer <- 
    st_transform(QnsMTA, ('ESRI:102318')) %>% 
      st_buffer(1320) %>%
      dplyr::select(name)

QnsMTA_tracts16 <- 
  st_join(tracts16, grad_buffer) %>%
  filter(!is.na(name))

# Map mean average of MedRent variable within 1/4 miles of MTA stations

pop_station <- QnsMTA_tracts16 %>% 
  group_by(name) %>%
  summarize(sumTotalPop = sum(TotalPop)) %>%
  st_drop_geometry() %>%
  left_join(QnsMTA) %>%
  st_sf()

ggplot() +
  geom_sf(data = allTracts.group, fill = "white") +
  geom_sf(data = pop_station, aes(size = sumTotalPop), shape = 21,
          fill = "#0868ac", alpha=0.5) +
  labs(title = "Population and Transit", subtitle = "Population Within 1/4 Mile of Queens, NY MTA Stations", caption ="Figure 5.1") +
  scale_size_continuous(range = c(.5, 15))

# Map mean average of MedRent variable within 1/4 miles of MTA stations

rent_station <- QnsMTA_tracts16 %>% 
  group_by(name) %>%
  summarize(avgRent = mean(MedRent, na.rm = TRUE)) %>%
  st_drop_geometry() %>%
  left_join(QnsMTA) %>%
  st_sf()

ggplot() +
  geom_sf(data = allTracts.group, fill = "white") +
  geom_sf(data = rent_station, aes(size = avgRent), shape = 21,
          fill = "#38885e", alpha=0.5) +
  labs(title = "Median Rent and Transit", subtitle = "Average Rent Within 1/4 Mile of Queens, NY MTA Stations", caption ="Figure 5.2") +
  scale_size_continuous(range = c(.5, 15))

```

### Part 6: Median Rent by Distance from TOD Area

Interestingly, contrary to the general understanding of how TOD affects local rent, on Queen the median rent increases as one travels farther from the subway station. Again, this may be due in part to the larger homes that exist in the more suburban neighborhoods of inner and eastern Queens. Future analyses may choose to control for property size by mapping median rent per square foot.

```{r Part 6. Line Plot as Function of Distance, echo=FALSE}

QnsBoundary <- st_union(tracts16)

ring_buffer <- multipleRingBuffer(buffer, 15840, 1320)

# Plot ring buffers

ggplot() + 
  geom_sf(data = QnsBoundary, fill = "lightgray", lwd = 1) +
  geom_sf(data = ring_buffer, fill = "white", alpha = 0.3) +
  geom_sf(data=QnsMTA, color = "#0868ac") +
  labs(title = "Distances from TOD Area", 
       subtitle = "1/4 Mile Ring Buffers", 
       caption ="Figure 6.0")

# Determine tracts that intersect with each ring buffer, 
# and calculate mean MedRent and distance from MTA station

allTracts.rings <- rbind(
  st_intersection(ring_buffer, allTracts.group) %>%
  st_drop_geometry() %>%
  group_by(distance, year) %>%
  mutate(Selection_Type = "Clip") %>%
  mutate(avgMedRent = mean(MedRent, na.rm = TRUE), 
         distance = distance / 5280, na.rm = TRUE))

# Graph Average Rent by Year and Distance from Subway Station

ggplot(data=allTracts.rings,
       aes(x = distance, y = avgMedRent, color = year)) +
  geom_point() +
  geom_line(size = 1.25) + 
  scale_x_continuous(breaks=seq(0, 2, by = 0.25)) +
  scale_y_continuous(labels = scales::dollar_format()) +
  xlab(label = "Distance from Subway (miles)") +
  ylab(label = "Avg. Median Income (by Tract)") +
  labs(title = "Average Rent by Distance from Subway",
       subtitle = "1/4 Mile Ring Buffers",
       caption ="Figure 6.1") +
  plotTheme()

```

### Part 7: Robbery, Transit, and Median Rent

Robbery complaints to the NYPD in 2016 shows a clear geographic correlation with transit access, and less of an assocation with median rent. The neighborhoods with the lowest rates of robbery, unsurprisingly, are in the more suburban parts of Queens, where there is little or no subway and bus access.

```{r Part 7. 2016 Crime Data: Robbery, echo=FALSE, message=FALSE, warning=FALSE}

# Read crime data in from GitHub .csv file (manually filtered down from 6.9M rows to ~2,900 rows,
# showing only robberies in Queens in 2016)
QNSrobbery16 <- 
  rbind(
    read.csv("/Users/julianazhou/Documents/GitHub/MUSA508_TOD_QueensNY/NYPD_Complaint_Data_2016.csv") %>% 
    dplyr::select(OFNS_DESC, VIC_RACE, VIC_SEX, Y = Latitude, X = Longitude) %>%
    na.omit() %>%
  st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant")) 

ggplot()+
  geom_sf(data = st_union(tracts16))+
  geom_sf(data = tracts16, aes(fill = q5(MedRent)), lwd = 0) +
  geom_sf(data = QNSrobbery16, show.legend = "point", size= .5, alpha = 0.5) +
  geom_sf(data = buffer, fill = "transparent", color = "red", lwd = 1) +
  scale_fill_manual(values = palette5,
                    labels = qBr(allTracts.group, "MedRent"),
                    name = "Robberies") +
  labs(title = "Robberies in 2016", subtitle = "# of Complaints to NYPD") +
  coord_sf(crs = st_crs(2263)) +
  mapTheme() + 
  theme(plot.title = element_text(size=22))
```


[^longnote]: *Data Sources:*
    
    * Tract-level data from American Community Survey, 5-year estimates
    * MTA station data from NYC Open Data
    * 2016 robbery complaint data from NYC Open Data
